% -*- coding: utf-8 -*-
%-------------------------
% Resume in Latex
% Author : Jing Wan
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
%\usepackage[UTF8]{ctex} %for latex
\usepackage{fontspec}
\usepackage{xeCJK}
\setCJKmainfont{Source Han Serif CN}
%\input{glyphtounicode} %for latex
\XeTeXgenerateactualtext=1

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
%\pdfgentounicode=1 %for latex

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\setlength{\footskip}{5pt}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Mark Wan (万晶)} \\ \vspace{1pt}
    \small 156-0198-1011 $|$ \href{mailto:wanjingjjj@gmail.com}{\underline{wanjingjjj@gmail.com}} $|$ 
    \href{https://github.com/wanjingjjj}{\underline{github.com/wanjingjjj}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Shanghai Jiaotong University}{Shanghai}
      {Bachelor of Biology}{Sep. 2003 -- Jun. 2007}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Adevinta (ebay classifieds group)}{Shanghai}
      {Sr. Staff Engineer(L26)}{Nov. 2020 -- Present}
      \resumeItemListStart
        \resumeItem{Design and maintain the data platform based on Airflow and Spark running on \emph{EKS}.}
	\resumeItem{Develop and maintain in house Spark version with \emph{AWS} glue, delta.io, multi-arch, and cloud native support.}
        \resumeItem{Lead and develop in house Notebook solution using \emph{React} and \emph{go} based on Jupyter and VSCode.}
        \resumeItem{Review and optimize the \emph{AWS} cloud cost to meet the budget.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {CraiditX}{Shanghai}
      {Data Engineering Manager}{Sep. 2018 -- Oct. 2020}
      \resumeItemListStart
        \resumeItem{Lead the team on developing the data product for bank customers.}
        \resumeItem{On site deploy data product on customer's on-premise infrastructure.} 
        \resumeItem{Coordination on people resource and communication between multiple projects.}
      \resumeItemListEnd

      \resumeSubSubheading
          {Sr. Data Engineer}{Jun. 2015 -- Aug. 2018}
          \resumeItemListStart
          \resumeItem{Created the data warehouse platform from scratch by using airflow and CDH on \emph{AWS}.}
          \resumeItem{Created an unified data log service to collect data from site application.}
          \resumeItem{Created BI dashboard by using Superset. BU also have the flexibility to explore and create new report by self-service.}
          \resumeItem{Transform data and generate features for machine learning data model applications.}
          \resumeItemListEnd
      
    \resumeSubheading
      {ebay}{Shanghai}
      {Sr. Software Engineer(L24)}{Mar. 2011 -- May. 2015}
      \resumeItemListStart
        \resumeItem{Developed and maintained billing analytic data pipelines using \emph{UC4(Appworx)} and \emph{SAS}.}
        \resumeItem{Maintain and batch support on bi-monthly ebay billing run.}
        \resumeItem{Developed self-service tools to help BU to retrieve data from billing system.}
        \resumeItem{Automated workflow for billing operations.}
      \resumeItemListEnd

    \resumeSubheading
      {Alibaba Group}{Hangzhou}
      {ETL Engineer}{Sep. 2010 -- Mar. 2011}
      \resumeItemListStart
        \resumeItem{Developed and maintained data warehouse platform for \emph{Ali-Finance}.}
        \resumeItem{Created data pipelines to generate features for online credit loan AI model.}
      \resumeItemListEnd

    \resumeSubheading
      {ebay (dx solution contractor)}{Shanghai}
      {DW Developer}{Jul. 2007 -- Sep. 2010}
      \resumeItemListStart
        \resumeItem{Build ETL process on \emph{ebay} Teradata platform.}
        \resumeItem{SQL tunning and batch support on data warehouse data pipelines.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Notebook Scheduling} $|$ \emph{AWS(EKS), Kubernetes, Argo Workflow, React, Go}}{Jul. 2023 -- Jun. 2024}
          \resumeItemListStart
            \resumeItem{Use \emph{Argo Workflow} to run jupyter notebook files recurrently.}
            \resumeItem{Use \emph{kubernetes operator} to store and manage the schedules.}
            \resumeItem{Web interface provided to let the user manage all the schedules.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{DWH Migration} $|$ \emph{AWS(EKS, S3, Glue), Airflow, Spark, Kubernetes, Python}}{Jun. 2021 -- Jun. 2023}
          \resumeItemListStart
            \resumeItem{Use EKS as the foundation of the infrastructure, Airflow as the workflow orchestration engine, Spark as the main process engine. All services are cloud native.}
            \resumeItem{Created base docker image containing all of the tool chains and ETL handlers, which provided as the default run time of the all ETL jobs.}
            \resumeItem{Created Spark image with patches to connect to \emph{AWS Glue} as hive metastore. All }
            \resumeItem{Design and implement the CI/CD service for the new platform.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{AI Data Service} $|$ \emph{Python, Go, CDH(Hive), Java}}{Jun. 2016 -- Aug. 2018}
          \resumeItemListStart
            \resumeItem{Use Python / Go to build backend data service to serve the online ML model.}
            \resumeItem{Create data logging service to capture the intermedia and final result from ML model, which will be stored on Hadoop.}
            \resumeItem{Process the data from log, along with other sources offline on Hadoop using hive.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL (SparkSQL / Hive), Go, Java, JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: Spark, Hadoop, Flask, pandas, Matplotlib, Airflow, Argoflow, React, Beego, Springboot } \\
     \textbf{Developer Tools}{: Git, Kubernetes (EKS), Docker, AWS, Terraform, Datadog, Grafana} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
